Implementing Real-Time Transport Services over an Ossified Network

### 2016-06-22 paper.tex
Use normal font size
Add todo about labels in Table 3
Update formatting of Section 2

Table \ref{tab:services} summarises the transport services discussed in this
Section, and required for real-time multimedia applications.
%--------------------------------------------------------------------------------------------------
\subsection{Timing and Transport Services}

The work in TAPS provides a vocabulary for discussing the components of
transport protocols.  The vocabulary is useful when discussing the needs of
real-time applications, and the protocols to support them.

Timing is the most salient feature of real-time applications. Since their data
must be conveyed with real-time demands, they all have some concept of a
\emph{deadline}. Data that fails to present within the deadline is otherwise
useless.
% Deadlines may be short or long.
The `slack' in a deadline depends on the application. Interactive applications,
such as telephony, video conferencing, or telepresence, require low end-to-end
latency. Their deadlines for presenting the media, \ie playing the audio and
displaying the video frame, range from tens to a few hundred milliseconds.
Non-interactive application deadlines associated with broadcast and on-demand
programming are on the order of seconds.
% , such as broadcast TV, may have deadlines on the order of seconds,
% or even tens of seconds for on-demand programming.

@@

\subsection{Partial Reliability}
In a best-effort network, deadlines
constrain packet delivery service to \emph{partial reliability}.
%The network has non-zero probability of losing any particular packet.
For example, when used to repair loss, the limits of forward error correction
imply some probability that packet will be non-recoverable. By contrast,
retransmissions used to recover from loss have potentially unbounded delay
(since any retransmission may itself be lost).
% These probabilities can be estimated, to give probabilistic constraints on
% loss and delay, but will be non-zero. Accordingly, to meet deadlines the
Accordingly, a transport protocol that meets deadlines should provide partial
reliability, acknowledging that it may be unable to deliver all data by its
deadline.

@@

\subsection{Message-oriented Dependencies}

The combination of deadlines and partial reliability leads to \emph{dependency
management} as an important transport service.
% There is no point in sending data that cannot be used because it depends on
% previous data that was not received.
In particular, data should never be sent when it relies on a previous
transmission that was never received. Providing this service is complicated by
the two ways in which data can be \emph{useful} to applications: it may itself
be played out, or it may be needed as part of the application's decoding chain.
Interdependencies between frames of video exist within a number of codecs,
including MPEG-1 \cite{le1991mpeg}, and newer codecs such as H.264
\cite{wiegand2003overview}. As an example, we consider MPEG-1 video:
I-frames are independent, while P- and B-frames contain only the changes 
since the previous frame (P) or between frames (B), and so are dependent on
the successful arrival of other frames. An I-frame may not arrive in time
to be played out, but may need to be sent to ensure that dependent P- and
B-frames are useful.

@@

\subsection{Connection and Congestion Control}

We note the importance of congestion control. %Clearly,
Historically real-time applications needed an isochronous channel,
and needed to avoid subjected to congestion control. This is impractical on the
Internet. Further, while some applications are non-adaptive or constant bitrate,
an increasing number are either or both of adaptive and variable bitrate.
Users would be better served by applications that adapt to available bandwidth.

@@

\begin{table*}
  \small

@@

\begin{table}
  \centering
    \begin{tabular}{llcc}
    \toprule
    & ISP & Port 4001 & Port 80 \\ \midrule
    \textbf{Fixed-line} & Andrews \& Arnold & \pass & \pass \\
    & BT & \pass & \pass \\
    & Demon & \pass & \pass \\
    & EE & \pass & \pass \\
    & Eclipse & \pass & \pass \\
    & Sky & \pass & \pass \\
    & TalkTalk & \pass & \pass \\
    & Virgin Media & \pass & \pass \\ \midrule
    \textbf{Cellular} & EE & \okay & \okay \\
    & O2 & \okay & \okay \\
    & Three & \pass & \pass \\
    & Vodafone & \pass & \okay \\
    \bottomrule
    \end{tabular}
  \caption[]{Deployability of inconsistent retransmissions, where \pass \thinspace
  indicates successful delivery, \okay \thinspace indicates delivery of the original
  data, and \fail \thinspace indicates connection failure (none observed)}
  \label{tab:deployability}
\end{table}

>>>>

%--------------------------------------------------------------------------------------------------
\subsection{Desirable Transport Services}

The work in TAPS provides a vocabulary for discussing the components of
transport protocols. The vocabulary is useful when discussing the needs 
of real-time applications, and the protocols to support them. In this 
section, we use this to describe the transport services we believe are
required for real-time multimedia applications.
Table \ref{tab:services} summarises the transport services discussed.

\textbf{Timing and Deadlines:}
Timing is the most salient feature of real-time applications. Since their data
must be conveyed with real-time demands, they all have some concept of a
\emph{deadline}. Data that fails to present within the deadline is otherwise
useless.
% Deadlines may be short or long.
The `slack' in a deadline depends on the application. Interactive applications,
such as telephony, video conferencing, or telepresence, require low end-to-end
latency. Their deadlines for presenting the media, \ie playing the audio and
displaying the video frame, range from tens to a few hundred milliseconds.
Non-interactive application deadlines associated with broadcast and on-demand
programming are on the order of seconds.
% , such as broadcast TV, may have deadlines on the order of seconds,
% or even tens of seconds for on-demand programming.

@@

\textbf{Partial Reliability:}
In a best-effort network, deadlines
constrain packet delivery service to \emph{partial reliability}.
%The network has non-zero probability of losing any particular packet.
For example, when used to repair loss, the limits of forward error correction
imply some probability that packet will be non-recoverable. By contrast,
retransmissions used to recover from loss have potentially unbounded delay
(since any retransmission may itself be lost).
% These probabilities can be estimated, to give probabilistic constraints on
% loss and delay, but will be non-zero. Accordingly, to meet deadlines the
Accordingly, a transport protocol that meets deadlines should provide partial
reliability, acknowledging that it may be unable to deliver all data by its
deadline.

@@

\textbf{Message-oriented Dependencies:}
The combination of deadlines and partial reliability leads to \emph{dependency
management} as an important transport service.
% There is no point in sending data that cannot be used because it depends on
% previous data that was not received.
In particular, data should never be sent when it relies on a previous
transmission that was never received. Providing this service is complicated by
the two ways in which data can be \emph{useful} to applications: it may itself
be played out, or it may be needed as part of the application's decoding chain.
Interdependencies between frames of video exist within a number of codecs,
including MPEG-1 \cite{le1991mpeg}, and newer codecs such as H.264
\cite{wiegand2003overview}. As an example, we consider MPEG-1 video:
I-frames are independent, while P- and B-frames contain only the changes 
since the previous frame (P) or between frames (B), and so are dependent on
the successful arrival of other frames. An I-frame may not arrive in time
to be played out, but may need to be sent to ensure that dependent P- and
B-frames are useful.

@@

\textbf{Connection and Congestion Control:}
We note the importance of congestion control. %Clearly,
Historically real-time applications needed an isochronous channel,
and needed to avoid subjected to congestion control. This is impractical on the
Internet. Further, while some applications are non-adaptive or constant bitrate,
an increasing number are either or both of adaptive and variable bitrate.
Users would be better served by applications that adapt to available bandwidth.

@@

\begin{table*}[t]

@@

\begin{table}
  \centering
    \begin{tabular}{llcc}
    \toprule
    & ISP & Port 4001 & Port 80 \\ \midrule
    \textbf{Fixed-line} & Andrews \& Arnold & \pass & \pass \\
    & BT & \pass & \pass \\
    & Demon & \pass & \pass \\
    & EE & \pass & \pass \\
    & Eclipse & \pass & \pass \\
    & Sky & \pass & \pass \\
    & TalkTalk & \pass & \pass \\
    & Virgin Media & \pass & \pass \\ \midrule
    \textbf{Cellular} & EE & \okay & \okay \\
    & O2 & \okay & \okay \\
    & Three & \pass & \pass \\
    & Vodafone & \pass & \okay \\
    \bottomrule
    \end{tabular}
  \caption[]{Deployability of inconsistent retransmissions, where \pass \thinspace
  indicates successful delivery, \okay \thinspace indicates delivery of the original
  data, and \fail \thinspace indicates connection failure (none observed)}
  \todo{the labels need to be distinctive shapes, not just different colours}
  \label{tab:deployability}
\end{table}
